The transition redshift as a probe of reionization

### 2019-08-14 paper/ms.tex
Update about surface brightness calc

In detail $N_{\Ha}$ will have a frequency-dependent structure, but for
$z\sim9$ to $10$, it is reasonable to assume a conservative, constant value of
$N_{\Ha}\sim4\times10^4\,\text{Jy}/\text{sr}$ for the medium survey. For
$N_{21}$, we assume that $N_{21} = P_{21,21}(k=0.1\,\text{Mpc}^{-1})$, a
reasonable approximation given that HERA-350 will image some large scale modes
\citep{2017PASP..129d5001D}, as discussed previously \citep{2018ApJ...867...26B}.

>>>>

In detail the surface brightness sensitivity will have a frequency-dependent
structure, but for $z\sim9$ to $10$, it is reasonable to assume a
conservative, constant value of
$\sigma_{\Ha}\sim4\times10^4\,\text{Jy}/\text{sr}$ for the medium survey. To
convert the surface brightness sensitivity to a power spectrum noise, we simply
write,
\beq \label{eq:ps_}
N_{\Ha} = \sigma_{\Ha}^2 V_{\text{voxel}}\text{,}
\eeq 
where $V_{\text{voxel}}$ is the comoving volume of one voxel. To compute this
we use the fact that CDIM will have $1''$ pixels and a resolution of $R=300$.

For
$N_{21}$, we assume that $N_{21} = P_{21,21}(k=0.1\,\text{Mpc}^{-1})$, a
reasonable approximation given that HERA-350 will image some large scale modes
\citep{2017PASP..129d5001D}, as discussed previously \citep{2018ApJ...867...26B}.
